Perceptions and Preferences for Meritocracy

### 2020-06-10 docs/paper.Rmd
ajustes
- aumento tamañode las  letras en las  tablas

- cambio _config.yml para imagenes

- agrego bibliografia sugerida

b. Beliefs: the "get ahead" battery refers to "how important you think it is", considered by Mijs as a belief in meritocracy. Nevertheless, another version of this same battery asks about "how important you think it _should_ be". Which one of both is the "belief"? If we consider belief as related to a normative content, actually the more close version is the "should be", being the other one more close to the perception of the situation. Such distinction was already made by @duru-bellat_whos_2012, who used the item "how important should the number of years spent in education and training be in deciding how much money people ought to earn?" for "desired" meritocracy, whereas for "perceived" meritocracy they use two items: “Would you say that in your country, people are rewarded for their efforts?” and “... people are rewarded for their skills?”. Is the belief in meritocracy a perception or a preference? A comprehensive measurement should be in line with what @duru-bellat_whos_2012 did, in order to open up possibilities of analyzing whether perceptions and preferences are actually the same (i.e. correlation close to 1) or they are different aspects of the same phenomenon. Therefore, two main drawbacks of the term "beliefs" are that (i) it hides different operationalizations of the concept of meritocracy, and (ii) it blurs the distinction between perceptions and preferences. We argue that perceptions and preferences should be disentangled and used together, specially when analyzing preferences. As @son_hing_merit_2011-1 have pointed out, "People can believe that outcomes ought to be distributed on the basis of merit and yet vary in their perceptions of whether this is how society currently operates" (p. 435). In other words, preferences should be interpreted in the context of perception: a large preference for meritocracy certainly means something totally different for someone perceiving high meritocracy than for someone perceiving low meritocracy.

@@

 kable(tab01,table_format,booktabs = T, linesep = "",col.names = cnames, caption = tb) %>%
   kable_styling(full_width = T,latex_options = c("hold_position","scale_down"),position = "center",font_size = 9) %>%
   column_spec(column = 1,width = "1.5cm",) %>%
   column_spec(column = 2,width = "2 cm") %>%
   collapse_rows(columns = 1:2,valign = "middle")

@@

![`r diam1`](../input/images/app_mod.png){ width=80% }

@@

```{r echo=FALSE}
load(file = "input/data/proc/dat04.RData")
dat04b<- dat04 %>% rename("A.Perception Effort" =perc_effort,
                          "B.Perception Talent" = perc_talent,
                          "C.Perception rich parents" = perc_wpart,
                         "D.Perception contacts" = perc_netw,
                          "E.Preferences Effort" = pref_effort,
                          "F.Preferences Talent" =  pref_talent, 
                         "G.Preferences rich parents" =  pref_wpart ,
                          "H.Preferences contacts" = pref_netw  )
sum04b  <- psych::describe(dat04b[,-c(1)], fast = T) %>% select(mean,sd,min,max) %>% data.frame() %>% round(digits = 2)
table04b<- sum04b %>% rename("Mean"=mean, "SD"=sd, "Min"=min,"Max"=max)
sumdat04<- kable(table04b,format =table_format, booktabs= T, escape = FALSE,align = "l",linesep = "", caption = tades
) %>% kable_styling(full_width = table_format2, font_size = 9,position = "center");sumdat04
```

@@

tb.fm01<- kable(tb.fm, format = table_format, booktabs = T,linesep = "", escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = loadfit) %>% 
          kable_styling(full_width = table_format2,latex_options = c("hold_position","scale_down"), position = "center",font_size = 9) %>% 
          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12))  %>%
          footnote(general = tb.foot,threeparttable = T);tb.fm01

>>>>

b. Beliefs: the "get ahead" battery refers to "how important you think it is", considered by Mijs as a belief in meritocracy. Nevertheless, another version of this same battery asks about "how important you think it _should_ be". Which one of both is the "belief"? If we consider belief as related to a normative content, actually the more close version is the "should be", being the other one more close to the perception of the situation. Such distinction was already made by @duru-bellat_whos_2012, who used the item "how important should the number of years spent in education and training be in deciding how much money people ought to earn?" for "desired" meritocracy, whereas for "perceived" meritocracy they use two items: “Would you say that in your country, people are rewarded for their efforts?” and “... people are rewarded for their skills?”. Is the belief in meritocracy a perception or a preference? A comprehensive measurement should be in line with what @duru-bellat_whos_2012 did, in order to open up possibilities of analyzing whether perceptions and preferences are actually the same (i.e. correlation close to 1) or they are different aspects of the same phenomenon. Therefore, two main drawbacks of the term "beliefs" are that (i) it hides different operationalizations of the concept of meritocracy, and (ii) it blurs the distinction between perceptions and preferences. We argue that perceptions and preferences should be disentangled and used together, specially when analyzing preferences. As @son_hing_merit_2011-1 have pointed out, "People can believe that outcomes ought to be distributed on the basis of merit and yet vary in their perceptions of whether this is how society currently operates" (p. 435). In other words, preferences should be interpreted in the context of perception: a large preference for meritocracy certainly means something totally different for someone perceiving high meritocracy than for someone perceiving low meritocracy.Incorporating this conceptual difference could improve the accuracy of empirical analyzes that work with the concept of meritocratic beliefs in general [eg.  @MeritocraticNarrativesCulturaOrientations].

@@

 kable(tab01,table_format,booktabs = T, linesep = "",col.names = cnames, caption = tb) %>%
   kable_styling(full_width = T,latex_options = c("hold_position","scale_down"),position = "center",font_size = 12) %>%
   column_spec(column = 1,width = "1.5cm",) %>%
   column_spec(column = 2,width = "2 cm") %>%
   collapse_rows(columns = 1:2,valign = "middle")

@@

![`r diam1`](../input/images/app_mod.png){ width=90% }

@@

```{r echo=FALSE}
load(file = "input/data/proc/dat04.RData")
dat04b<- dat04 %>% rename("A.Perception Effort" =perc_effort,
                          "B.Perception Talent" = perc_talent,
                          "C.Perception rich parents" = perc_wpart,
                         "D.Perception contacts" = perc_netw,
                          "E.Preferences Effort" = pref_effort,
                          "F.Preferences Talent" =  pref_talent, 
                         "G.Preferences rich parents" =  pref_wpart ,
                          "H.Preferences contacts" = pref_netw  )
sum04b  <- psych::describe(dat04b[,-c(1)], fast = T) %>% select(mean,sd,min,max) %>% data.frame() %>% round(digits = 2)
table04b<- sum04b %>% rename("Mean"=mean, "SD"=sd, "Min"=min,"Max"=max)
sumdat04<- kable(table04b,format =table_format, booktabs= T, escape = FALSE,align = "l",linesep = "", caption = tades
) %>% kable_styling(full_width = table_format2, font_size = 12,position = "center");sumdat04
```

@@

tb.fm01<- kable(tb.fm, format = table_format, booktabs = T,linesep = "", escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = loadfit) %>% 
          kable_styling(full_width = table_format2,latex_options = c("hold_position","scale_down"), position = "center",font_size = 12) %>% 
          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12))  %>%
          footnote(general = tb.foot,threeparttable = T);tb.fm01
